\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\eps}{\tilde{\epsilon}}
\newcommand{\phist}{\tilde{\varphi}^*}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}

\title{The Extension Graph of Spoof Lehmer Factorizations\\
Is a Forest}
\author{G.\ Molnar}
\date{\today~(Draft)}

\begin{document}
\maketitle

\begin{abstract}
Hasanalizade recently showed that, given a spoof factorization~$F$
satisfying $k\phist(F) = \eps(F) + \alpha$ for $\alpha = \pm 1$, the search
for two-factor extensions $F \cdot x \cdot y$ satisfying the $k$-Lehmer
condition $k\phist(F \cdot x \cdot y) = \eps(F \cdot x \cdot y) - 1$
reduces to a single integer factorization.  We study the global structure
that this extension operation imposes on the set of $k$-Lehmer
factorizations.  We prove three results: (i)~positive-integer extensions
arise exclusively from $\alpha = +1$ seeds, (ii)~the descent
formula relating the evaluation of a Lehmer factorization to any descended
pair is \emph{independent of~$k$}, and (iii)~the resulting extension
graph~$\mathcal{G}_k$ is a \textbf{forest} for \emph{every}
$k \ge 2$---that is, no $k$-Lehmer factorization with factors~$\ge 2$
admits more than one descended pair.  A computational census for
$k = 2$ classifies all~$39$ factorizations reachable through seeds with at
most six factors, identifies exactly~$9$ primitive factorizations, and
reveals $17$~plus-seeds, of which only six belong to the Fermat
partial-product chain.
\end{abstract}


%=====================================================================
\section{Introduction}
%=====================================================================

Molnar and Singh~\cite{MS26} introduced the study of \emph{spoof Lehmer
factorizations}: multisets $F = \{x_1, \ldots, x_r\}$ of positive integers
satisfying
\begin{equation}\label{eq:lehmer}
  k\,\phist(F) = \eps(F) - 1,
  \qquad k \in \Z_{>0},
\end{equation}
where $\eps(F) = \prod x_i$ and $\phist(F) = \prod (x_i - 1)$.
Hasanalizade~\cite{H26} proved that if a factorization~$F$ satisfies the
auxiliary condition $k\,\phist(F) = \eps(F) + \alpha$ for
$\alpha \in \{-1, +1\}$, then the search for two-factor extensions
$F \cdot x \cdot y$ satisfying~\eqref{eq:lehmer} reduces to factoring a
single explicit integer (Equation~\eqref{eq:hasanalizade} below).

This note investigates the global structure that the Hasanalizade extension
imposes on the solution set.  The main contributions are:
\begin{enumerate}[label=(\roman*)]
  \item A proof that only $\alpha = +1$ seeds can produce extensions with
    positive factors (Theorem~\ref{thm:positive-only}).
  \item A closed-form descent criterion
    (Theorem~\ref{thm:descent-formula}) and the observation that it
    is \emph{independent of~$k$} (Corollary~\ref{cor:k-free}).
  \item A proof that the extension graph~$\mathcal{G}_k$ is a forest
    for every $k \ge 2$ (Theorem~\ref{thm:forest}).
  \item A computational census for $k = 2$ classifying
    primitives and plus-seeds (Theorem~\ref{thm:census}).
\end{enumerate}


%=====================================================================
\section{Preliminaries}
%=====================================================================

We follow the notation of~\cite{MS26} and~\cite{H26}.  A \emph{spoof
factorization} is a finite multiset $F = x_1 \cdots x_r$ of positive
integers with $x_i \ge 2$, with \emph{spoof evaluation}
$\eps(F) = \prod x_i$ and \emph{spoof unitary totient}
$\phist(F) = \prod(x_i - 1)$.  We write $|F| = r$ for the number of
factors.  A factorization~$F$ with $|F| \ge 2$ is \emph{unitary $k$-Lehmer}
if~\eqref{eq:lehmer} holds.

\begin{definition}\label{def:seed}
A factorization~$F$ is an \emph{$\alpha$-seed} (with respect to~$k$) if
$k\,\phist(F) = \eps(F) + \alpha$, where $\alpha \in \{-1, +1\}$.  When
$\alpha = +1$, we call $F$ a \emph{plus-seed}.
\end{definition}

Hasanalizade's Theorem~3 in~\cite{H26} states that if~$F$ is an
$\alpha$-seed with $N = \eps(F)$, then $F \cdot x \cdot y$ is $k$-Lehmer
if and only if
\begin{equation}\label{eq:hasanalizade}
  (\alpha x - N - \alpha)(\alpha y - N - \alpha) = N^2 + \alpha N - \alpha.
\end{equation}

We also use the \emph{deficiency function} $g(F) = k\,\phist(F) - \eps(F)$,
which satisfies the recurrence
\begin{equation}\label{eq:recurrence}
  g(F \cdot a) = (a-1)\,g(F) - \eps(F), \qquad g(\emptyset) = k - 1.
\end{equation}
Lehmer factorizations correspond to $g = -1$, plus-seeds to $g = 1$.


%=====================================================================
\section{Only plus-seeds produce positive extensions}
%=====================================================================

\begin{theorem}\label{thm:positive-only}
Let $k \ge 2$ and let~$F$ be a $(-1)$-seed with $\eps(F) = N \ge 1$.  Then
Equation~\eqref{eq:hasanalizade} has no solutions with $x, y \ge 2$.
\end{theorem}

\begin{proof}
For $\alpha = -1$, Equation~\eqref{eq:hasanalizade} becomes
$(x + N - 1)(y + N - 1) = N^2 - N + 1$.  If $x, y \ge 2$ then the left
side is at least $(N+1)^2 = N^2 + 2N + 1 > N^2 - N + 1$ for all
$N \ge 1$.
\end{proof}


%=====================================================================
\section{The descent formula is $k$-independent}
%=====================================================================

\begin{definition}\label{def:descent}
Let~$G$ be a $k$-Lehmer factorization.  An unordered pair $\{a, b\}$ of
factors of~$G$ (counted with multiplicity) is a \emph{descended pair} if
$F = G \setminus \{a, b\}$ is a plus-seed from which~$G$ arises via
Equation~\eqref{eq:hasanalizade}.  We call~$G$ \emph{primitive} if
it admits no descended pair, and \emph{derived} otherwise.
\end{definition}

\begin{theorem}[Descent formula]\label{thm:descent-formula}
Let $k \ge 2$ and let~$G$ be a $k$-Lehmer factorization with
$\eps(G) = N$.  An unordered pair $\{a, b\}$ of factors of~$G$ is a
descended pair if and only if
\begin{equation}\label{eq:descent}
  N(a + b - 1) = ab\bigl((a-1)(b-1) + 1\bigr).
\end{equation}
\end{theorem}

\begin{proof}
The sub-factorization $F = G \setminus \{a, b\}$ has
$\eps(F) = N/(ab)$ and $\phist(F) = \phist(G)/\bigl((a-1)(b-1)\bigr)$.
Since~$G$ is $k$-Lehmer and~$F$ is a plus-seed:
\[
  k\,\phist(F) = \frac{k\,\phist(G)}{(a-1)(b-1)} = \frac{N-1}{(a-1)(b-1)},
  \qquad
  k\,\phist(F) = \frac{N}{ab} + 1.
\]
Equating:
\begin{equation}\label{eq:k-cancels}
  \frac{N - 1}{(a-1)(b-1)} = \frac{N}{ab} + 1.
\end{equation}
Clearing denominators: $(N-1)\,ab = N(a-1)(b-1) + ab(a-1)(b-1)$.
Expanding $N(a-1)(b-1) = N(ab - a - b + 1)$ and collecting:
\[
  N(a + b - 1) = ab\bigl(ab - a - b + 2\bigr) = ab\bigl((a-1)(b-1)+1\bigr).
  \qedhere
\]
\end{proof}

\begin{corollary}[$k$-independence]\label{cor:k-free}
The descent formula~\eqref{eq:descent} is independent of~$k$.
Equivalently, whether a pair $\{a,b\}$ can be a descended pair is
determined entirely by the multiset of factors and the evaluation~$N$, not
by the value of~$k$.
\end{corollary}

\begin{proof}
Equation~\eqref{eq:k-cancels} shows that $k$ cancels in the passage from
the $k$-Lehmer and plus-seed conditions to~\eqref{eq:descent}.
\end{proof}

\begin{remark}
The $k$-independence is perhaps surprising: the Lehmer condition $k\phist =
\eps - 1$ and the plus-seed condition $k\phist = \eps + 1$ both involve~$k$
explicitly, but dividing the first by the second at the level of a
descended pair absorbs~$k$ into the relationship between $\{a,b\}$ and
the remaining factors.
\end{remark}


%=====================================================================
\section{The extension graph is a forest}
%=====================================================================

\begin{definition}
The \emph{extension graph} $\mathcal{G}_k$ is a directed graph whose
vertices are the $k$-Lehmer factorizations with factors $\ge 2$.  There is
an edge $G \to F$ whenever~$F = G \setminus \{a, b\}$ for some descended
pair $\{a, b\}$.
\end{definition}

\begin{theorem}[Forest theorem]\label{thm:forest}
For every $k \ge 2$, the extension graph~$\mathcal{G}_k$ is a forest:
every $k$-Lehmer factorization with factors $\ge 2$ admits at most one
descended pair.
\end{theorem}

By Corollary~\ref{cor:k-free}, the descent formula~\eqref{eq:descent} is
$k$-independent, so the entire proof reduces to showing that no single
multiset~$G$ with $\eps(G) = N$ can have two distinct unordered pairs
satisfying~\eqref{eq:descent} with an appropriate divisibility and
positivity structure.  The proof uses three lemmas, covering the three
possible cases for the intersection of two descended pairs.

\begin{lemma}[Disjoint case]\label{lem:disjoint}
Let~$G$ be a $k$-Lehmer factorization.  Then~$G$ cannot admit two
descended pairs $\{a,b\}$ and $\{c,d\}$ with
$\{a,b\} \cap \{c,d\} = \emptyset$.
\end{lemma}

\begin{proof}
Write $G = \{a, b, c, d\} \cup E$ with $\eps(E) = Q$ (where $Q = 1$ if
$E = \emptyset$), so $N = abcdQ$.  Applying the descent
formula~\eqref{eq:descent} to each pair and dividing by~$ab$ and~$cd$
respectively:
\begin{align}
  \label{eq:dj-I}
  cdQ\,(a+b-1) &= (a\!-\!1)(b\!-\!1)+1, \\
  \label{eq:dj-II}
  abQ\,(c+d-1) &= (c\!-\!1)(d\!-\!1)+1.
\end{align}
Since $(a-1)(b-1) + 1 \le ab$ for $a,b \ge 2$ (with strict inequality
unless one of $a, b$ equals~$1$), multiplying gives
\[
  a^2b^2c^2d^2\,Q^2\,(a\!+\!b\!-\!1)(c\!+\!d\!-\!1) \le a^2b^2c^2d^2,
\]
whence $Q^2(a+b-1)(c+d-1) \le 1$.  Since $a+b-1 \ge 3$ and $c+d-1 \ge 3$,
we get $Q^2 \le 1/9 < 1$, so $Q < 1$.

If $E \ne \emptyset$ then $Q \ge 2$, a contradiction.  If
$E = \emptyset$ then $Q = 1$ and~\eqref{eq:dj-I}--\eqref{eq:dj-II} become
$cd(a+b-1) = (a-1)(b-1)+1$ and $ab(c+d-1) = (c-1)(d-1)+1$.  The first
gives $cd < ab/(a+b-1) \le ab/3$; the second gives $ab < cd/(c+d-1) \le
cd/3$.  Together: $cd < ab/3 < cd/9$, which is absurd.
\end{proof}


\begin{lemma}[Overlapping case]\label{lem:overlap}
Let~$G$ be a $k$-Lehmer factorization.  Then~$G$ cannot admit two
descended pairs $\{a,b\}$ and $\{b,d\}$ sharing one element, where
$a \ne d$.
\end{lemma}

\begin{proof}
Write $G = \{a, b, d\} \cup E$ with $\eps(E) = Q$, so $N = abdQ$.  The
descent formula for each pair gives
\begin{align}
  \label{eq:ov-I}
  dQ\,(a+b-1) &= (a\!-\!1)(b\!-\!1)+1, \\
  \label{eq:ov-II}
  aQ\,(b+d-1) &= (b\!-\!1)(d\!-\!1)+1.
\end{align}
Bounding: $dQ \le ab/(a+b-1)$ and $aQ \le bd/(b+d-1)$.  Multiplying:
\[
  adQ^2 \le \frac{ab^2d}{(a+b-1)(b+d-1)},
  \qquad\text{so}\qquad
  Q^2 \le \frac{b^2}{(a+b-1)(b+d-1)}.
\]
We claim $(a+b-1)(b+d-1) > b^2$ for all $a,b,d \ge 2$.  Expanding:
\begin{align*}
  (a+b-1)(b+d-1) - b^2
    &= a(b+d-1) + b(d-2) + (1-d) \\
    &\ge 2(b+d-1) + 0 + (1-d)
    = 2b+d-1
    \ge 3.
\end{align*}
Therefore $Q^2 < 1$, which is impossible if $E \ne \emptyset$ (since then
$Q \ge 2$).

If $E = \emptyset$, then $|G| = 3$, $Q = 1$, and~$G = \{a,b,d\}$.  The
seed of $\{a,b\}$ is the single-element factorization~$(d)$, and the
plus-seed condition $k(d-1) = d + 1$ gives $d = (k+1)/(k-1)$.  By
symmetry, the seed of $\{b,d\}$ forces $a = (k+1)/(k-1)$.  We consider
three sub-cases:
\begin{itemize}
  \item $k = 2$: $d = a = 3$, $G = \{3, b, 3\}$, $N = 9b$.  The Lehmer
    condition $2 \cdot 2(b-1) \cdot 2 = 9b - 1$ gives $8b - 8 = 9b - 1$,
    hence $b = -7$.
  \item $k = 3$: $d = a = 2$, $G = \{2, b, 2\}$, $N = 4b$.  The Lehmer
    condition $3 \cdot 1 \cdot (b-1) \cdot 1 = 4b - 1$ gives
    $3b - 3 = 4b - 1$, hence $b = -2$.
  \item $k \ge 4$: $(k+1)/(k-1)$ is not an integer (since $k - 1 \ge 3$
    and $\gcd(k-1, k+1) \mid 2$), so no single-element plus-seed exists
    and the $|G| = 3$ case is vacuous.
\end{itemize}
In all cases, no valid factorization arises.
\end{proof}


\begin{lemma}[Repeated-element case]\label{lem:repeated}
Let~$G$ be a $k$-Lehmer factorization.  Then~$G$ cannot admit descended
pairs $\{v,v\}$ and $\{v,w\}$ with $w \ne v$, where $v$ appears with
multiplicity at least two in~$G$.
\end{lemma}

\begin{proof}
Write $G = \{v, v, w\} \cup E$ with $\eps(E) = Q$, so $N = v^2 wQ$.  The
descent formula for the pair~$\{v,v\}$ gives, after dividing by~$v^2$:
\begin{equation}\label{eq:rep-key}
  wQ(2v-1) = (v-1)^2 + 1.
\end{equation}
The left side is a positive multiple of $2v - 1$, so
$(2v-1) \mid \bigl((v-1)^2 + 1\bigr)$.  We compute modulo $2v-1$: since
$2(v-1) \equiv -1 \pmod{2v-1}$,
\[
  4\bigl((v-1)^2 + 1\bigr) = (2v-2)^2 + 4 \equiv 1 + 4 = 5 \pmod{2v-1}.
\]
As $\gcd(4, 2v-1) = 1$, we conclude $(2v-1) \mid 5$, giving
$2v - 1 \in \{1, 5\}$ and $v \in \{1, 3\}$.

For $v = 3$: Equation~\eqref{eq:rep-key} gives $5wQ = 5$, so $wQ = 1$,
forcing $w = 1$ and $Q = 1$.  But factors must be $\ge 2$.

For $v = 1$: factors must be $\ge 2$.

Neither case yields a valid factorization.
\end{proof}


\begin{proof}[Proof of Theorem~\ref{thm:forest}]
Let~$G$ be a $k$-Lehmer factorization with factors $\ge 2$, and suppose
for contradiction that $\{a,b\}$ and $\{c,d\}$ are two distinct descended
pairs.  There are three cases:
\begin{itemize}
  \item $\{a,b\} \cap \{c,d\} = \emptyset$: impossible by
    Lemma~\ref{lem:disjoint}.
  \item $|\{a,b\} \cap \{c,d\}| = 1$ with distinct values: after
    relabeling, $\{a,b\}$ and $\{b,d\}$ with $a \ne d$, impossible by
    Lemma~\ref{lem:overlap}.
  \item $|\{a,b\} \cap \{c,d\}| = 1$ with a repeated element: $\{v,v\}$
    and $\{v,w\}$, impossible by Lemma~\ref{lem:repeated}.
\end{itemize}
The only remaining possibility $\{a,b\} = \{c,d\}$ contradicts the
assumption that the pairs are distinct.
\end{proof}

\begin{corollary}\label{cor:unique-seed}
For any $k \ge 2$, every derived $k$-Lehmer factorization is produced
by a unique plus-seed.
\end{corollary}


%=====================================================================
\section{Computational census for $k = 2$}
%=====================================================================

\begin{theorem}[Census]\label{thm:census}
For $k = 2$, the following hold among all $2$-Lehmer factorizations
reachable through plus-seeds with at most six factors.
\begin{enumerate}[label=(\alph*)]
  \item There are exactly~$17$ plus-seeds with $|F| \le 6$ (including
    $\emptyset$).  Six belong to the Fermat partial-product chain and
    eleven are sporadic (Table~\ref{tab:seeds}).
  \item The resulting~$39$ Lehmer factorizations include exactly~$9$
    primitives (Table~\ref{tab:primitives}) and~$30$ derived
    factorizations.
  \item The number of derived factorizations produced by a plus-seed~$F$
    equals the number of divisor pairs of $\Delta_+(N) = N^2 + N - 1$,
    where $N = \eps(F)$.
\end{enumerate}
\end{theorem}

\begin{proof}
By exhaustive enumeration using the recurrence~\eqref{eq:recurrence}.
Starting from $g(\emptyset) = 1$, factors are added with the constraint
that $g$ remains a positive integer at every non-terminal step.  The search
space is bounded by Hasanalizade's Theorem~1.  The forest property is
confirmed \emph{a posteriori} (and now also \emph{a priori} by
Theorem~\ref{thm:forest}).
\end{proof}

\begin{table}[ht]
\centering
\caption{Plus-seeds for $k = 2$ with $|F| \le 6$.}\label{tab:seeds}
\smallskip
\begin{tabular}{@{}clrl@{}}
\toprule
$|F|$ & Seed $F$ & $\eps(F)$ & Type \\
\midrule
0 & $\emptyset$ & 1 & Fermat \\
1 & $(3)$ & 3 & Fermat \\
2 & $(3, 5)$ & 15 & Fermat \\
3 & $(3, 5, 17)$ & 255 & Fermat \\
4 & $(3, 5, 17, 257)$ & 65\,535 & Fermat \\
  & $(5, 5, 5, 43)$ & 5\,375 & Sporadic \\
5 & $(3, 5, 17, 257, 65537)$ & $4.29 \times 10^9$ & Fermat \\
  & $(3, 5, 17, 353, 929)$ & $8.36 \times 10^7$ & Fermat-ext. \\
  & $(3, 9, 9, 23, 131)$ & $7.32 \times 10^5$ & Sporadic \\
  & $(5, 5, 5, 43, 5377)$ & $2.89 \times 10^7$ & Sporadic \\
  & $(5, 5, 5, 47, 453)$ & $2.66 \times 10^6$ & Sporadic \\
  & $(5, 7, 7, 7, 133)$ & $2.28 \times 10^5$ & Sporadic \\
6 & $(3, 9, 9, 23, 131, 732161)$ & $5.36 \times 10^{11}$ & Sporadic \\
  & $(3, 11, 11, 11, 677, 3659)$ & $9.89 \times 10^{9}$ & Sporadic \\
  & $(5, 5, 5, 53, 215, 158265)$ & $2.25 \times 10^{11}$ & Sporadic \\
  & $(5, 7, 7, 7, 133, 228097)$ & $5.20 \times 10^{10}$ & Sporadic \\
  & $(5, 7, 7, 13, 13, 619)$ & $2.56 \times 10^{7}$ & Sporadic \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Primitive $2$-Lehmer factorizations.}\label{tab:primitives}
\smallskip
\begin{tabular}{@{}clr@{}}
\toprule
$|G|$ & Primitive $G$ & $\eps(G)$ \\
\midrule
5 & $(5, 5, 5, 43, 5375)$ & $2.89 \times 10^7$ \\
5 & $(5, 5, 9, 9, 89)$ & $1.80 \times 10^5$ \\
6 & $(3, 5, 17, 377, 1217, 2295)$ & $2.69 \times 10^{11}$ \\
6 & $(3, 5, 17, 395, 1059, 2303)$ & $2.46 \times 10^{11}$ \\
6 & $(3, 5, 33, 53, 69, 8343)$ & $1.51 \times 10^{10}$ \\
6 & $(3, 9, 9, 23, 131, 732159)$ & $5.36 \times 10^{11}$ \\
6 & $(5, 5, 5, 47, 457, 50659)$ & $1.36 \times 10^{11}$ \\
6 & $(5, 5, 5, 65, 129, 2325)$ & $2.44 \times 10^{9}$ \\
6 & $(5, 7, 7, 7, 133, 228095)$ & $5.20 \times 10^{10}$ \\
\bottomrule
\end{tabular}
\end{table}


%=====================================================================
\section{The Fermat chain and sporadic seeds}
%=====================================================================

The Fermat partial products $F^{(s)} = \prod_{i=0}^{s-1}(2^{2^i}+1)$
form a linear chain of plus-seeds for $k = 2$, since the telescoping
identity
\[
  2\prod_{i=0}^{s-1} 2^{2^i}
    = 2^{2^s}
    = \prod_{i=0}^{s-1}(2^{2^i}+1) + 1
\]
gives $2\,\phist(F^{(s)}) = \eps(F^{(s)}) + 1$.  Each seed generates
Lehmer factorizations by factoring
$\Delta_+(2^{2^s}\!-\!1) = 2^{2^{s+1}} - 2^{2^s} - 1$.

However, the Fermat chain accounts for only~$6$ of the~$17$ plus-seeds in
our census.  One seed, $(3, 5, 17, 353, 929)$, bridges the two worlds:
it arises from the Fermat seed $(3,5,17)$ via a
\emph{seed-to-seed extension}, solving
$(x - 256)(y - 256) = 255^2 + 255 - 1 = 65279 = 97 \cdot 673$ to give
$x = 353$ and $y = 929$.  This suggests a secondary recursive structure on
the set of plus-seeds themselves---a direction for future work.

\begin{figure}[ht]
\centering
\begin{tikzpicture}[
  seed/.style={draw, rounded corners, fill=gray!15, minimum width=1.5cm,
    font=\footnotesize, align=center, inner sep=3pt},
  lehmer/.style={draw, fill=white, minimum width=1.5cm, font=\footnotesize,
    align=center, inner sep=3pt},
  arr/.style={-{Stealth}, thick},
  scale=0.85, transform shape
]
\node[seed] (s0) at (0,0) {$\emptyset$};
\node[lehmer] (l1) at (0,-1.4) {$(3,3)$};
\node[seed] (s1) at (2.5,0) {$(3)$};
\node[lehmer] (l2) at (2.5,-1.4) {$(3,5,15)$};
\node[seed] (s2) at (5,0) {$(3,5)$};
\node[lehmer] (l3) at (5,-1.4) {$(3,5,17,$\\$255)$};
\node[seed] (s3) at (8,0) {$(3,5,17)$};
\node[lehmer] (l4a) at (7,-1.4) {$(3,5,17,$\\$257,65535)$};
\node[lehmer] (l4b) at (9.5,-1.4) {$(3,5,17,$\\$285,2507)$};

\draw[arr] (s0) -- (l1);
\draw[arr] (s1) -- (l2);
\draw[arr] (s2) -- (l3);
\draw[arr] (s3) -- (l4a);
\draw[arr] (s3) -- (l4b);

\node[seed] (sp1) at (3,-3.2) {$(5,5,5,43)$\\sporadic};
\node[lehmer] (sp1a) at (0.5,-5) {$(5,5,5,43,$\\$8507,14605)$};
\node[lehmer] (sp1b) at (3,-5) {$\cdots$ {\tiny(7 more)}};
\node[lehmer] (sp1c) at (5.8,-5) {$(5,5,5,43,$\\$5377,$\\$28901375)$};
\draw[arr] (sp1) -- (sp1a);
\draw[arr] (sp1) -- (sp1b);
\draw[arr] (sp1) -- (sp1c);

\node[lehmer, dashed, thick] (prim) at (9.5,-3.8) {$(5,5,9,9,89)$\\
  {\tiny primitive}};
\end{tikzpicture}
\caption{A fragment of~$\mathcal{G}_2$.  Rounded: plus-seeds.
Solid: derived Lehmer factorizations.  Dashed: primitive.}\label{fig:tree}
\end{figure}


%=====================================================================
\section{Open questions}
%=====================================================================

\begin{enumerate}[label=\arabic*.]
  \item \textbf{Finiteness of primitives.}  All nine known primitive
    $2$-Lehmer factorizations have $|G| \ge 5$.  Are there finitely many
    for each~$k$?

  \item \textbf{Realizability.}  Which spoof factorizations correspond
    to actual integers $n = p_1^{\alpha_1} \cdots p_r^{\alpha_r}$ with
    each $x_i = p_i^{\alpha_i}$ a prime power?

  \item \textbf{Sporadic seed structure.}  Is there a generating mechanism
    for the sporadic plus-seeds, or a secondary recursive structure
    explaining their proliferation?

  \item \textbf{Density of primitives.}  Among our~$39$ factorizations,
    $9$~are primitive (${\approx}23\%$).  Does this proportion converge?
\end{enumerate}


\begin{thebibliography}{9}

\bibitem{H26}
E.~Hasanalizade, \emph{Some remarks on a paper of Molnar and Singh},
Integers \textbf{26} (2026).

\bibitem{L32}
D.~H.~Lehmer, \emph{On Euler's totient function}, Bull.\ Amer.\ Math.\
Soc.\ \textbf{38} (1932), 745--751.

\bibitem{MS26}
G.~Molnar and G.~Singh, \emph{Spoof Lehmer factorizations}, Integers
\textbf{26} (2026), \#A33.

\bibitem{N15}
P.~Nielsen, \emph{Odd perfect numbers, Diophantine equations, and upper
bounds}, Math.\ Comp.\ \textbf{84} (2015), 2549--2567.

\end{thebibliography}

\end{document}
